---
title: "PerryLetters"
---

Textual Analysis
Corpi: Benjamin F. Perry Letters and Elizabeth Frances McCall Perry Letters
Collections located at the South Caroliniana Archive
Transcribed by Allen Stokes (retired director of South Caroliniana)

Load Text Anaylsis/Tidy Data libraries
```{r}
#install.packages("tidytext")
#install.packages("readtext")
#install.packages("widyr")
#install.packages("SnowballC")
```

Seems to work better if you install the packages one at a time, rather than how I coded it above. Maybe should just run install.packages() directly on the command line?

```{r}
library("tidyverse")
library("tidytext") 
library("readtext")
library("widyr")
library("SnowballC")
```

Load BFPerryTranscribedLetters txt document and use readtext to :

```{r}
BFPLetters_file_path <- "/Users/crboatwright/PerryLetters/BFPerryTranscribedLetters.txt"
BFPLetters_text_data <- readtext(BFPLetters_file_path)
head(BFPLetters_text_data)
```

Tokenize the text by word:
- This also makes the text lowercase and removed punctuation

```{r}
tidy_BFPLetters <- BFPLetters_text_data %>%
    unnest_tokens(word, text)

tidy_BFPLetters
```

Tokenize by sentence:

```{r}
tidy_BFPLetters_sentences <- BFPLetters_text_data %>%
    unnest_tokens(sentence, text, token = "sentences")

tidy_BFPLetters_sentences
```

Error above. Probably because dataframe isn't property formatted.

